A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-11 skeleton_and_pathtracing.tex
Corrections a partir de l'article dechire de vence (ne dechire pas celui-ci vence)

Informally, in 3d, a set of faces $X$ is a complex if each side (square) of a cube of $X$ also belong to $X$, each edge of a square of $X$ also belong to $X$, and each vertex of an edge of $X$ also belong to $X$.

A face $f \in X$ is \myem{a facet of $X$} if $f$ is not a proper face of any face of $X$. We denote by $\princ{X}$ the set composed of all facets of $X$ . A complex $X$ is \myem{pure} if all its facets have the same dimension. The \myem{dimension of $X$} is $\mydim{X} = \max\{\mydim{f} \suchthat f \in X\}$. If $\mydim{X} = d$, then we say that $X$ is a $d$-complex.

@@

Different definitions of the orientation and direction can be given, corresponding to different order of removal of free faces in the complex and leading to different results.
Algorithm~\ref{algo::pardircollapse_v0} can be implemented to run in linear time complexity (proportionally to the number of faces of the complex). Indeed, checking if a face is free or not may be easily done in constant time. Moreover, when a free pair $(f,g)$ is removed from the input complex, it is sufficient to scan the elements of $\cellstrict{f}$ in order to find new free faces.

@@

\subsection{The lifespan of a face}
In the following, we define more notions in the cubical complex. The first one we present is the \myem{death date} of a face.

@@

These three values are dependant on the order of direction and orientation chosen for Alg.~\ref{algo::pardircollapse_v0}.

The lifespan of a face $f$ of $X$ indicates how many "rounds" this face "survives" as a facet in $X$, when removing free faces with Alg.~\ref{algo::pardircollapse_v0}. 
The lifespan is a good indicator of how important a face can be in an object. Typically, higher the lifespan is, and more representative of an object's visual feature the face is. The lifespan, sometimes called \myem{saliency}, was used in \cite{Liu2009} (with the name "medial persistence") in order to propose a thinning algorithm in cubical complexes based on two parameters.

\subsection{Distance map, opening function and decenterness map}
\label{subsec::distmap}
In addition to the lifespan of a face, the proposed homotopic thinning method uses information on distance between faces in order to decide if a face should be kept safe from deletion. We define hereafter the various notions needed for this, based on distance in the voxel framework.

>>>>

%Informally, in 3d, a set of faces $X$ is a complex if each side (square) of a cube of $X$ also belong to $X$, each edge of a square of $X$ also belong to $X$, and each vertex of an edge of $X$ also belong to $X$.

A face $f \in X$ is \myem{a facet of $X$} if $f$ is not a proper face of any face of $X$. We denote by $\princ{X}$ the set composed of all facets of $X$. The \myem{dimension of $X$} is $\mydim{X} = \max\{\mydim{f} \suchthat f \in X\}$. If $\mydim{X} = d$, then we say that $X$ is a $d$-complex.

@@

Different definitions of orientation and direction can be given, each corresponding to a different order of free faces removal in the complex and leading to different results.
Algorithm~\ref{algo::pardircollapse_v0} can be implemented to run in linear time complexity (proportionally to the number of faces in the complex). Indeed, checking if a face is free or not may be easily done in constant time. Moreover, when a free pair $(f,g)$ is removed from the input complex, it is sufficient to scan the elements of $\cellstrict{f}$ in order to find new free faces.

@@

\subsection{The lifespan of a face}
In the following, we define additional functions in the cubical complex, which are essential for the filtering step of the skeleton. The first one we present is the \myem{death date} of a face.

@@

These three values depend on the order of direction and orientation chosen for Alg.~\ref{algo::pardircollapse_v0}.

The lifespan of a face $f$ of $X$ indicates how many "rounds" this face "survives" as a facet in $X$, when removing free faces with Alg.~\ref{algo::pardircollapse_v0}, and is a good indicator of how important a face can be in an object. Typically, the higher the lifespan is, and the more representative of an object's visual feature the face is. The lifespan, sometimes called \myem{saliency}, was used in \cite{Liu2009} (with the name "medial persistence") in order to propose a thinning algorithm in cubical complexes based on two parameters.

\subsection{Distance map, opening function and decenterness map}
\label{subsec::distmap}
In addition to the lifespan of a face, the proposed homotopic thinning method uses information on distance between faces in order to decide if a face should be kept safe from deletion. We define hereafter various notions based on distances in the voxel framework.
